\documentclass[noanswers]{exam}

\newcommand{\myroot}{../../..}
\usepackage[hw]{\myroot/course}
\title{Assignment \#2: Computer vision}
\author{\usnaAuthorShort}
%\date{\printdate{\hwZeroOut}}
%\duedate{\printdate{\hwzeroDue}}
\date{\today}
\duedate{\printdate{1/30/2020}}

\begin{document}
\maketitle

For all assignments, upload a copy of the assignment as a \Google\ document to \GoogleClassroom\ and rename it with the assignment name and team member’s last name.  For example:
\begin{lstlisting}
2-computer-vision-evangelista-binzel
\end{lstlisting}



\begin{questions}
\question
\textbf{Problem statement and background research.}  Review your feedback from your problem statement and background research assignment.  Incorporate any updates or deficiencies.

\question
\textbf{Computer vision subsection.} Introduce the camera and explain why it is needed.  Include a schematic and/or photo. Utilize captions and annotations to explain to the reader how the camera is mounted on the auto-turret and how you power the camera. Additionally, you must address the following points in your write-up.  Keep in mind that a reader should be able to duplicate your results based on your presentation.
\begin{itemize}
\item What camera is used for the vision processing?
\item Explain \textbf{in your own words} (don’t just regurgitate the instructions) the process of getting an image into \Matlab.  
\item For the image you worked with, how did you process it (only show the stuff you do care about)
\item How did you select the correct target?
\item How did you validate that your process works for different targets?
\item Where you have variables that you will tweak for the final demo (minArea, eccentricity, etc.) and give an example of typical values used in testing.
\item Include your \Matlab\ code as an enclosure or in an Appendix and place your code in an appropriate Github repository for future use.
\end{itemize}

All assignments must also include a critical analysis of your procedure, implementation, and results for full credit.  If you had any issues, explain your troubleshooting process and lessons learned.

\question
\textbf{Statement of contribution.} Since a majority of the work in the class is done as a team, it is also important to identify the individual contributions of team member.  For each assignment, include a description and percentage of each team member’s contribution. 
\end{questions}
\end{document}

