\documentclass[noanswers]{exam}

\newcommand{\myroot}{../../..}
\usepackage[hw]{\myroot/course}
\title{Assignment \#0: Team selection, lab station, and locker assignment}
\author{\usnaAuthorShort}
%\date{\printdate{\hwZeroOut}}
%\duedate{\printdate{\hwzeroDue}}
\date{\today}
\duedate{\printdate{1/13/2020}}

\begin{document}
\maketitle

For all assignments, upload a copy of the assignment as a PDF or \Google\ document to \GoogleClassroom\ and rename it with the assignment name and team member’s last name.  For example:
%0. Team selection_Lab station_Locker Asssignment_EvangelistaBinzel
\begin{lstlisting}
0-team-selection-lab-station-locker-assignment-evangelista-binzel
\end{lstlisting}

\begin{questions}
\question Form your project teams.  There should be two people on each team (with the exception of an odd number of students in a section which would require a team of three).  

Keep in mind that his course requires significant \Matlab\ and C++ coding, design of a position controller for a DC motor, firing circuit development, and lots of patience for troubleshooting when your system doesn’t working as planned.  There are also multiple writing assignments and a final design report. With these in mind, you may want to choose a partner that complements your strengths so that together you have a team that is confident and competent in most of the areas of this course.
\begin{solution}[2in]
\end{solution}

\question Find a lab station.  This will be your station for the entire semester.  You will also work with the turret, gun, power supply, and camera that is located at this station.  Do \textbf{not} under any circumstances move any of the equipment at that station unless told to do so by your instructor.  
\begin{solution}[1in]
\end{solution}

\question
Pick a locker and note the number of the lock on the locker.  You will be given the combination of the lock that is on your locker.  Write it down somewhere so that you don’t forget it.  Better yet -- \textbf{write it down and then take a picture of what you wrote}.  You will probably lose the piece of paper but most of you don’t go anywhere without your phones.  
\begin{solution}[1in]
\end{solution}

\question
Please provide all the above information in a PDF or \Google\ document and upload to your \GoogleClassroom\ folder.    
\end{questions}
\end{document}

